Quantum Oracles - How to Transform Classical Problems into Quantum ones

### 2024-07-31 latex/paper.tex
finished grover and sets difference

\documentclass{article}
\usepackage{arxiv}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{hyperref}      
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}      
\usepackage{cleveref}       
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{caption}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage{titlesec}
\usepackage[rightcaption]{sidecap}

@@

Ao utilizar as rotações específicas para cada bit-string, é possível conseguir melhores resultados ao medir os valores na saída, se sobressaindo em relação a rotação padrão.

\begin{center}
	\includegraphics[scale=0.4]{new-grover-test-different-bit-strings-with-optimal-angles.png}
	\captionof{figure}{Teste utilizando os melhores ângulos de cada bit-string em bit-strings diferentes}
	\label{fig:best-angles-diff-bit-strings-grover}
\end{center}

No entanto, ao utilizar esses valores com outras bit-strings, os resultados não conseguem alcançar tal limiar, além modificar as outras probabilidades de forma irregular. Sendo assim, a rotação convencional é a melhor na maioria das vezes.\\
Além disso, para bit-strings de dois bits, utilizar a superposição dada por $H$ se mostra a melhor alternativa.

\begin{center}
	\includegraphics[scale=0.5]{classical_grover_for_1_bit_strings_l2_outcomes.png}
	\captionof{figure}{Resultado Grover padrão encodado uma bit-string de 2 bits}
	\label{fig:l2-grover-classical-outcomes}
\end{center}

\begin{center}
	\includegraphics[scale=0.5]{new_grover_for_1_bit_strings_l2_outcomes.png}
	\captionof{figure}{Resultado Grover modificado encodado uma bit-string de 2 bits}
	\label{fig:l2-grover-new-outcomes}
\end{center}

Com isso, para ter o melhor dos dois mundos, foi usado uma versão híbrida do algoritmo. Assim, para criar o circuito, é passado o valor a ser encodado por uma Hash-Table com os ângulos otimizados. Dessa forma, é possível maximizar as probabilidades de encontrar, nesse caso, o arquivo que está sendo procurado.

\subsubsubsection{Diferença de conjuntos}
Sobrepondo dois Phase Oracles distintos, com ranges de valores diferentes, é realizada a operação de diferença entre conjuntos \cite{sanchezrivero2023initial}.

\begin{center}
	\includegraphics[scale=0.3]{less_than.png}
	\captionof{figure}{Exemplo - diferença de conjuntos}
	\label{fig:less-than-circuit}
\end{center}

Nesse exemplo \ref{fig:less-than-circuit} foi encodado no primeiro Oracle o set $\{000, 001, 010, 0110\}$ e no segundo $\{000, 001, 010, 011, 100, 101\}$.

\begin{center}
	\includegraphics[scale=0.5]{less_than_unitary.png}
	\captionof{figure}{Resultado da diferença de conjuntos}
	\label{fig:less-than-circuit-unitary}
\end{center}

Ao sobrepô-los \ref{fig:less-than-circuit-unitary}, apenas os valores $\{100, 101\}$ permaneceram com a fase, representando então a sobreposição delas.

>>>>

\documentclass{article}
\usepackage{arxiv}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{hyperref}      
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}      
\usepackage{cleveref}       
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{caption}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage{titlesec}
\usepackage[rightcaption]{sidecap}
\usepackage{wrapfig}

@@

Using specific rotations for each bit-string, it's possible to improve the outcomes, and even stand out the default rotation.

\begin{center}
	\includegraphics[scale=0.4]{new-grover-test-different-bit-strings-with-optimal-angles.png}
	\captionof{figure}{Test Using the best angles of each bit-string in different ones}
	\label{fig:best-angles-diff-bit-strings-grover}
\end{center}

However, using the best angle of a distinct bit-string as the source of superposition in the algorithm, isn't enough to overcome the classical Grover implementation, and also the probability distribution becomes irregular. So, for a general purpose implementation, the default rotation is the best one for the most part of the cases. This behavior is even weird with $2$ Qubits, being the $H$ gate rotation the best ever for that.

\begin{center}
	\includegraphics[scale=0.5]{classical_grover_for_1_bit_strings_l2_outcomes.png}
	\captionof{figure}{Results for Grover with 2 Qubits (default rotation)}
	\label{fig:l2-grover-classical-outcomes}
\end{center}

\begin{center}
	\includegraphics[scale=0.5]{new_grover_for_1_bit_strings_l2_outcomes.png}
	\captionof{figure}{Results for Grover with 2 Qubits (modified rotation)}
	\label{fig:l2-grover-new-outcomes}
\end{center}

For our purpose in this project, a hybrid algorithm was done. So during the circuit setup, the searched value pass through a Hash-Table will optimal angles. This way, the algorithm can achieve better outcomes at the end of the execution, finding, this way, the file we want.

\subsubsubsection{Sets Difference}
Overlapping two distinct Phase Oracles, each one with a range of values encoded. The remaining Phases, are the difference of the sets encoded by them \cite{sanchezrivero2023initial}.

%FIX: cut the image a little bit on the left sie
%FIND A WAY TO PUT THESE TWO IMAGES ON THE SIDES OF THE PAGE

\begin{center}
	\centering
	\includegraphics[scale=0.3]{less_than.png}
	\captionof{figure}{Sets Difference Algorithm Example}
	\label{fig:less-than-circuit}
\end{center}

In the last example \ref{fig:less-than-circuit}, the set $\{000, 001, 010, 0110\}$ was encoded in the first Oracle and $\{000, 001, 010, 011, 100, 101\}$ in the second one.

\begin{center}
	\includegraphics[scale=0.4]{less_than_unitary.png}
	\captionof{figure}{Unitary After applying the Sets Difference algorithm}
	\label{fig:less-than-circuit-unitary}
\end{center}

After Overlapping the phases  \ref{fig:less-than-circuit-unitary}, only the values $\{100, 101\}$ keep the $-1$ value. This way, we can do the set operation just applying some oracles with the values.
